The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-11-18 sections/climate.tex
Some small changes for homogeneity

Our atmospheric forcing consists of monthly climatologies of surface air temperature and precipitation obtained from one observational dataset, three global reanalyses and one regional reanalysis.

>>>>

Our climate forcing consists of monthly climatologies of surface air temperature and precipitation obtained from one observational dataset, three global reanalyses and one regional reanalysis.

### 2013-11-18 sections/results.tex
Final comments from Arjen
Some small changes for homogeneity

Using WorldClim, NCEP/NCAR, ERA-Interim, CFSR (smoothed and original datasets) and NARR input climatologies as climate forcing, we run 66~simulations of glacial inception and growth of the Cordilleran ice sheet over 10~ka using temperature offsets ranging from 0 to 10\,\unit{\degree C}. Significant differences in patterns of ice sheet growth, final glacial extent, and volume are attained (Fig. \ref{fig:ivolarea}-\ref{fig:cool05}).

@@

Under present climate (0\,\unit{\degree C} offset), WorldClim, NARR and ERA-Interim forcing produce local ice caps in areas presently glaciated (Fig.~\ref{fig:extent}). These results are fairly consistent with contemporary ice distribution, although both the 10~km horizontal resolution and the occurrence of glaciers and ice caps surface topographies in the ETOPO1 dataset used for basal topography prevent a meaningful detailed comparison. CFSR forcing, on the other hand, yields continuous ice cover over the northern Coast Mountains, and NCEP/NCAR forcing results in ice sheet growth, both of which are largely inconsistent with the present state of glaciation. At the opposite side of the temperature offset range, it can be noted that both the NCEP/NCAR and CFSR forcing produce oversized ice sheets whose extents are primarily restricted by the domain boundaries (Fig.~\ref{fig:extent}). The smoothing of CFSR precipitation yields an insignificant effect on the resulting ice sheet geometry.

>>>>

Using WorldClim, NCEP/NCAR, ERA-Interim, CFSR (smoothed and original datasets) and NARR input climatologies as climate forcing, we run 66~simulations of glacial inception and growth of the Cordilleran ice sheet over 10~ka using temperature offsets ranging from 0 to 10\,\unit{\degree C}. Significant differences in patterns of ice sheet growth, final glacial extent, and volume are attained (Figs. \ref{fig:ivolarea}-\ref{fig:cool05}).

@@

Under present climate (0\,\unit{\degree C} offset), WorldClim, ERA-Interim and NARR forcing produce local ice caps in areas presently glaciated (Fig.~\ref{fig:extent}). These results are fairly consistent with contemporary ice distribution, although both the 10~km horizontal resolution and the occurrence of glaciers and ice caps surface topographies in the ETOPO1 dataset used for basal topography prevent a meaningful detailed comparison. CFSR forcing, on the other hand, yields continuous ice cover over the northern Coast Mountains, and NCEP/NCAR forcing results in ice sheet growth, both of which are largely inconsistent with the present state of glaciation. At the opposite side of the temperature offset range, it can be noted that both the NCEP/NCAR and CFSR forcing produce oversized ice sheets whose extents are primarily restricted by the domain boundaries (Fig.~\ref{fig:extent}). The smoothing of CFSR precipitation yields an insignificant effect on the resulting ice sheet geometry.
